### 2014-10-06 tex/proofs.tex
Removed r_f

\begin{theorem}[$\rsym$ preserves heap determinism]
\label{thm:determ}
Given a state, $s_\sym$, with a deterministic heap,
$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
\mathrm{heap}(s_\sym)$, the new heap,
$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
\mathrm{heap}(s_\sym^\prime)$, in any state related by the
symbolic relation, $s_\sym \rsym s_\sym^\prime$, is
also deterministic.
\end{theorem}
\begin{proof}
Proof by \lemref{FA-determ}, \lemref{FW-determ}, and \lemref{J-determ}
which represent all the rules that relate states in
$\rsym$.
\end{proof}

>>>>

\begin{theorem}[$\rsym$ preserves heap determinism]
\label{thm:determ}
Given a state, $s_\sym$, with a deterministic heap,
$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
\mathrm{heap}(s_\sym)$, the new heap,
$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
\mathrm{heap}(s_\sym^\prime)$, in any state related by the
symbolic relation, $s_\sym \rsym s_\sym^\prime$, is
also deterministic.
\end{theorem}
\begin{proof}
Proof by \lemref{lem:FA-determ}, \lemref{lem:FW-determ}, and \lemref{lem:J-determ}
which represent all the rules that relate states in
$\rsym$.
\end{proof}
